Instructions for developing new pages for the MarineOmics webpage

### 2023-12-15 DRAFT_DNA_methylation.Rmd
knit with bssnp R code
meth - added more bibtex - citations

The software used as part of this tutorial is **Bismark Bisulfite Mapper** (@10.1093/bioinformatics/btr167), which is one of the more widely-used softwares to align methylation data to a reference genome. Another commonly-used options include bwa-meth (@https://doi.org/10.48550/arXiv.1401.1129) and BSMAP (@https://doi.org/10.1186/1471-2105-10-232) (see @https://doi.org/10.1093/bib/bbab021 and @https://doi.org/10.1016/j.csbj.2022.08.051 for comparisons of these software for plant and mammal species, respectively). As with any software it is best to be famililar with the [User Manual](https://felixkrueger.github.io/Bismark/).

Within Bismark, the tutorial uses Bowtie 2 (@https://doi.org/10.1038/nmeth.1923) as the alignment software. Although the Bismark user manual covers the necessary Bowtie 2 parameters, it may be useful to refer to the [Bowtie 2 manual](https://bowtie-bio.sourceforge.net/bowtie2/manual.shtml).

@@

-   Feature overlap. Bedtools for quantitative assessment and IGV for visual assessment are valuable for thisl

>>>>

The software used as part of this tutorial is **Bismark Bisulfite Mapper** (@10.1093/bioinformatics/btr167), which is one of the more widely-used softwares to align methylation data to a reference genome. Another commonly-used options include bwa-meth (@pedersen2014fast) and BSMAP (@10.1186/1471-2105-10-232) (see @10.1093/bib/bbab021 and @10.1016/j.csbj.2022.08.051) for comparisons of these software for plant and mammal species, respectively). As with any software it is best to be famililar with the [User Manual](https://felixkrueger.github.io/Bismark/).

Within Bismark, the tutorial uses Bowtie 2 (@10.1038/nmeth.1923) as the alignment software. Although the Bismark user manual covers the necessary Bowtie 2 parameters, it may be useful to refer to the [Bowtie 2 manual](https://bowtie-bio.sourceforge.net/bowtie2/manual.shtml).

@@

-   Feature overlap. Bedtools for quantitative assessment and IGV for visual assessment are valuable for this.
